Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-04 minimax.tex
Solved pbl with autonum & hyperref
Hiding CCS

%\documentclass[sigconf]{aamas} 
\documentclass[sigconf, anonymous]{aamas}

@@

%%% The code below was generated by the tool at http://dl.acm.org/ccs.cfm.
%%% Please replace this example with code appropriate for your own paper.

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10010147.10010178.10010187</concept_id>
       <concept_desc>Computing methodologies~Knowledge representation and reasoning</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Knowledge representation and reasoning}

>>>>

\PassOptionsToPackage{hypertexnames=false, pdfusetitle, linkbordercolor={1 1 1}, citebordercolor={1 1 1}, urlbordercolor={1 1 1}}{hyperref}
%\documentclass[sigconf]{aamas} 
\documentclass[sigconf, anonymous]{aamas}

@@

%%% The code below was generated by the tool at http://dl.acm.org/ccs.cfm.
%%% Please replace this example with code appropriate for your own paper.
%TODO remove this before submission. This only serves to suppress the warning, but nobody seems to want this.
\settopmatter{printccs=false}
\ccsdesc[500]{Computing methodologies~Knowledge representation and reasoning}
